Using high-resolution variant frequencies to empower clinical genome interpretation

### 2016-10-12 manuscript/manuscript.Rmd

Secondly, it is often difficult to obtain accurate penetrance information for reported variants, and it is also difficult to know what degree of penetrance to expect or assume for newly discovered pathogenic variants. Although we would argue that variants with low penetrance have questionable diagnostic utility, our calculator app allows a user to define a range of compatible penetrance for a given allele frequency (see **Supplementary Methods**). Furthermore, methods to estimate variant penetrance from large case and control cohorts have been described previously`r citep("10.1126/scitranslmed.aad5169")`.

>>>>

Secondly, it is often difficult to obtain accurate penetrance information for reported variants, and it is also difficult to know what degree of penetrance to expect or assume for newly discovered pathogenic variants. Although we would argue that variants with low penetrance have questionable diagnostic utility, our calculator app allows a user to define a range of compatible penetrance for a given allele frequency (see **Supplementary Methods**). Furthermore, methods to estimate variant penetrance from large case and control cohorts have been described previously `r citep("10.1126/scitranslmed.aad5169")`.
